\documentclass{article}
\usepackage{url}
\usepackage{parskip}     
\usepackage{tabularx}
\usepackage{enumitem}
\usepackage{fontawesome5}
\usepackage{xcolor}
\usepackage[unicode, draft=false]{hyperref}
\usepackage[style=authoryear,sorting=ynt, maxbibnames=2]{biblatex}

% Centered version of 'X' col. type
\newcolumntype{C}{>{\centering\arraybackslash}X} 

% Custom section formatting
\usepackage{titlesec}
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{10pt}{10pt}

% Page setup
\usepackage[scale=0.9]{geometry}
\geometry{a4paper, total={170mm,257mm}, left=20mm, top=20mm}

% Setup hyperref package, and colours for links
\definecolor{linkcolour}{rgb}{0,0,0}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour}

\begin{document}

\begin{tabularx}{\linewidth}{@{} C @{}}
\Huge{Antara Paul}\\[5pt]
\href{https://github.com/Antara-Paul04}{\raisebox{-0.05\height}{\faGithub}\ Antara-Paul04} \ $|$ \ 
\href{https://www.linkedin.com/in/antara-paul-069a37271/}{\raisebox{-0.05\height}{\faLinkedin}\ Antara Paul} \ $|$ \ 
\href{https://antara-paul04.github.io/portfolio/}{\raisebox{-0.05\height}{\faGlobe}\ Portfolio} \ $|$ \ 
\href{mailto:paul.antara04@gmail.com}{\raisebox{-0.05\height}{\faEnvelope}\ paul.antara04@gmail.com} \ $|$ \ 
\href{tel:+000000000000}{\raisebox{-0.05\height}{\faMobile}\ +91 7602513009}\\
\end{tabularx}


\section{Work Experience}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{Google Developer Student Clubs (GDSC), Design Lead} & \hfill Aug 2023 - present \\[3pt]
Creative lead of GDSC IIITK 2023-24 chapter\\
Organized Rebase, overseeing all design branding aspects, including website design. \\[3pt]
\textbf{Free and Open Source Software (FOSS), Core Team Member} & \hfill Oct 2023 - present \\[3pt]
Organized meetups and actively contributed to community forums. \\[3pt]
\textbf{Google Developer Group (GDG) Kolkata, Volunteer} & \\[3pt]
Contributed to the organization team of DevFest 2023, including designing the event website. \\[3pt]
\textbf{Freelance Work} \\[3pt]
Engage in occasional freelance design projects \\
\end{tabularx}

\section{Projects}

\begin{tabularx}{\linewidth}{@{}l X@{}}
\Large\textbf{Design Projects} & \\[5pt]
\textbf{Rebase Hackathon:} & One of the lead organizers of Rebase, a hackathon. \\
& \textbf{Rebase Website:} \href{https://www.rebase01.tech/}{www.rebase01.tech} \\
& \textbf{Rebase Branding:} \href{https://www.behance.net/gallery/194027031/Rebase-brandingsocial-media}{Behance Gallery} \\[5pt]
\textbf{Devfest Kolkata 2023:} & Volunteered at GDG Kolkata and was a part of the organizing team for Devfest 2023, a prestigious tech conference. \\
& \textbf{Event Website:} \href{https://devfest.gdgkolkata.in/}{Devfest Kolkata 2023 Website}\\[3pt]
\multicolumn{2}{@{}X@{}}{My other projects are available on my \href{https://www.behance.net/antarapaul04}{\textbf{Behance}} and \href{https://dribbble.com/Paul_Antara}{\textbf{Dribbble}}} \\[3pt]
\Large\textbf{App Development Projects} & \\[5pt]
\textbf{Notes App:} & A simple notes application built using Flutter. \\
& \textbf{GitHub:} \href{https://github.com/Antara-Paul04/Notes-App}{Notes App Repository} \\[3pt]
\textbf{Todo App:} & A todo list application developed using Flutter. \\
& \textbf{GitHub:} \href{https://github.com/Antara-Paul04/To-Do-App}{Todo App Repository} \\[3pt]
\textbf{Twitter Clone (ongoing):} & Ongoing project to create a clone of the Twitter app using Flutter, Firebase and Riverpod. \\
& \textbf{GitHub:} \href{https://github.com/Antara-Paul04/Twitter-Clone}{Twitter App Repository} \\[3pt]
\textbf{Twitch Clone (ongoing):} & A project just started to create a clone of the Twitch app using Flutter, Firebase and Riverpod. \\
& \textbf{GitHub:} \href{https://github.com/Antara-Paul04/Twitch-Clone}{Twitch App Repository} \\[3pt]
\multicolumn{2}{@{}X@{}}{All my other projects are available on my \href{https://github.com/Antara-Paul04}{\textbf{GitHub Profile}}} \\
\end{tabularx}

\section{Education}
\begin{tabularx}{\linewidth}{@{}l X@{}}
2022 - 2026 & Computer Science and Engineering, IIIT Kalyani \hfill \normalsize (GPA(present): 8.4) \\
2022 & Class 12th (CBSE board) \\
2020 & Class 10th (ICSE board)\\
\end{tabularx}

\section{Skills}
\begin{tabularx}{\linewidth}{@{}l X@{}}
Design &  \normalsize{Figma, Adobe Illustrator, Blender.}\\
App Development  &  \normalsize{Dart, Flutter, Firebase}\\
Web Development  &  \normalsize{HTML, CSS, JS}\\  
Languages  &  \normalsize{Python, JAVA, C, Vivado}\\
Others &  \normalsize{Github, LaTeX}
\end{tabularx}

\end{document}
